Title

### 2025-03-06 Quarto Template.qmd
quarto template paths

```{r setup}
#| include: false
library(tidyverse)
library(redcapAPI)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/timvigers/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF")
```

@@

```{r}
#| label: tbl-planets
#| tbl-cap: Planets
```

@@

```{r}
#| label: fig-planets
#| fig-cap: Planets
```

>>>>

```{r setup}
#| include: false
library(tidyverse)
library(redcapAPI)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Documents/GitHub",
  "Linux" = "/home/timvigers/Documents/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
#| label: tbl-planets
#| tbl-cap: Planets

```

@@

```{r}
#| label: fig-planets
#| fig-cap: Planets

```
